---
title: "Detailed Example"
author: "Eliora Henzler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Detailed Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Specific test functions

## what is "all" in inspect_all?

`inspect_all()` wraps a number of specific data cleaning checks.
These can all be accessed directly as individual functions, outlined below.

## Load the cleaninginspectoR Package

```{r, results='hide', message=FALSE,warning=FALSE,error=FALSE}
library("cleaninginspectoR")
```

## Example data frame

Here we create some fake data for illustration purposes.
It is not important to understand this; we keep it in so you can run the example yourself if you like.
The dataset contains:

- variable `a`: random values and outliers
- variable `uuid`: values should be unique but are not
- variable `water.source.other`: all NA except for two
- variable `GPS.lat` just some numbers, but the column header indicates this is potentially sensitive


```{r}
testdf <- data.frame(a= c(runif(98),7287,-100),
                   b=sample(letters,100,T),
                   uuid=c(1:98, 4,20),
                   water.source.other = c(rep(NA,98),"neighbour's well","neighbour's well"),
                   GPS.lat = runif(100)
                   )
```

## Finding duplicates in certain columns 

There is a generic function to find duplicates in a certain specified column:

```{r,eval=F}
find_duplicates(testdf, duplicate.column.name = "uuid")
```

```{r,echo=F}
knitr::kable(find_duplicates(testdf, duplicate.column.name = "uuid"))
```

Often this is used on a column with UUID's, so there is a wrapper that looks for "uuid" in the column names and returns duplicates in the first matching column it finds. This gives the same result as the above:

```{r,eval=F}
find_duplicates_uuid(testdf)
```

```{r,echo=F}
knitr::kable(find_duplicates_uuid(testdf))
```

run `?find_duplicates` or `?find_duplicates_uuid` for details.

## Checking for outliers

```{r,eval=F}
find_outliers(testdf)
```

```{r,echo=F}
knitr::kable(find_outliers(testdf, duplicate.column.name = "uuid"))
```

Run `?find_outliers` for details

## Checking for other responses

```{r,eval=F}
find_other_responses(testdf)
```

```{r,echo=F}
knitr::kable(find_other_responses(testdf))

```

Run `?find_other_responses` for details

