---
title: "Quickstart"
author: "Eliora Henzler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the cleaninginspectoR library

```{r, results='hide', message=FALSE,warning=FALSE,error=FALSE}
library("cleaninginspectoR")
```


## Example data frame

Here we create some fake data for illustration purposes.
It is not important to understand this; we keep it in so you can run the example yourself if you like.
The dataset contains:

- variable `a`: random values and outliers
- variable `uuid`: values should be unique but are not
- variable `water.source.other`: all NA except for two
- variable `GPS.lat` just some numbers, but the column header indicates this is potentially sensitive


```{r}
testdf <- data.frame(a= c(runif(98),7287,-100),
                   b=sample(letters,100,T),
                   uuid=c(1:98, 4,20),
                   water.source.other = c(rep(NA,98),"neighbour's well","neighbour's well"),
                   GPS.lat = runif(100)
                   )
```


## Perform all available cleaning inspections

The function `inspect_all` runs all cleaning checks that are available.

```{r,eval=F}
inspect_all(testdf)
```
```{r,eval=T,echo=F}
kable(inspect_all(testdf))
```

## For unusual UUID column names

One of the things `inspect_all` does is to look for duplicates in the first column containing the word "uuid". If your ID column has a different name, you can specify it in the second parameter:

```{r,eval=F}
inspect_all(df = testdf,uuid.column.name = "b")
```

```{r,eval=T}
kable(inspect_all(df = testdf,uuid.column.name = "b"))
```


## More Details

For more information and individual check functions, see the [detailed example](detailed_example.html).
